### 2022-05-24 manuscript/manuscript.Rmd
edits to PRC figure

```{r generaltopicsfig, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 8, fig.height = 9, fig.cap = "Percentage of journals offering some statistical guidance (Panel A circles), having a dedicated statistical guidance section (Panel A diamonds), or offering guidance on each of twenty prespecified statistical topics (Panel B).  Black circles represent data for all journals overall (N = 330 journals). Coloured circles and diamonds in Panel A represent individual scientific disciplines (n = 15 journals). Data is in descending order by percentage (after overall data in Panel A). CCV in Panel B refers to categorizing continuous outcomes. Discipline abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE)."}

@@

plot_any_dedicated_joint + plot_all_topics & theme(plot.tag.position = c(0, 1),
        plot.tag = element_text(size = 14, hjust = 0, vjust = 0))

# to save individual plots for twitter
# ggsave(plot = plot_any_dedicated_joint, file = here('manuscript','figs','twitter','fig1A.png'), width = 6, height = 6.5, units = "in", dpi = 300)
# ggsave(plot = plot_all_topics, file = here('manuscript','figs','twitter','fig1B.png'), width = 6, height = 6.5, units = "in", dpi = 300)
```
```{r generaltopicsfignew, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 8, fig.height = 9, fig.cap = "Percentage of journals offering some statistical guidance (Panel A circles), having a dedicated statistical guidance section (Panel A diamonds), or offering guidance on each of twenty prespecified statistical topics (Panel B).  Black circles represent data for all journals overall (N = 330 journals). Coloured circles and diamonds in Panel A represent individual scientific disciplines (n = 15 journals). Data is in descending order by percentage (after overall data in Panel A). CCV in Panel B refers to categorizing continuous outcomes. Discipline abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE)."}
plot_any_dedicated_joint & theme(plot.tag.position = c(0, 1),
        plot.tag = element_text(size = 14, hjust = 0, vjust = 0))
```

>>>>

```{r prcfig, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 7, fig.height = 8, fig.cap = "Percentage of journals offering some statistical guidance (Panel A circles), having a dedicated statistical guidance section (Panel A diamonds), or offering guidance on each of twenty prespecified statistical topics (Panel B).  Black circles represent data for all journals overall (N = 330 journals). Coloured circles and diamonds in Panel A represent individual scientific disciplines (n = 15 journals). Data is in descending order by percentage (after overall data in Panel A). CCV in Panel B refers to categorizing continuous outcomes. Discipline abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE)."}

@@

# PEER REVIEW CONGRESS PLOT
plot_any_dedicated_joint + xlim(0,105) +ggtitle('A. General statistical guidance') + theme(axis.text.y = element_text(size = 10), plot.title.position = "plot", plot.title = element_text(hjust = 0)) + plot_all_topics + ggtitle('B. Specific statistical guidance') + theme(axis.text.y = element_text(size = 12), plot.title.position = "plot", plot.title = element_text(hjust = 0))

# to save individual plots for twitter
# ggsave(plot = plot_any_dedicated_joint, file = here('manuscript','figs','twitter','fig1A.png'), width = 6, height = 6.5, units = "in", dpi = 300)
# ggsave(plot = plot_all_topics, file = here('manuscript','figs','twitter','fig1B.png'), width = 6, height = 6.5, units = "in", dpi = 300)
```

```{r generaltopicsfignew, fig.path='figs/', dev=c('png', 'pdf'), fig.width = 8, fig.height = 9, fig.cap = "Percentage of journals offering some statistical guidance (Panel A circles), having a dedicated statistical guidance section (Panel A diamonds), or offering guidance on each of twenty prespecified statistical topics (Panel B).  Black circles represent data for all journals overall (N = 330 journals). Coloured circles and diamonds in Panel A represent individual scientific disciplines (n = 15 journals). Data is in descending order by percentage (after overall data in Panel A). CCV in Panel B refers to categorizing continuous outcomes. Discipline abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE)."}
plot_any_dedicated_joint & theme(plot.tag.position = c(0, 1),
        plot.tag = element_text(size = 14, hjust = 0, vjust = 0))
```
